\begin{itemize}
\item Chris Whittle, Ge Yang, Matthew Evans, Lisa Barsotti, \textit{Machine Learning for Quantum-Enhanced Gravitational-Wave Observatories}, Physical Review D, Volume 108, Article 043034. \href{https://arxiv.org/abs/2305.13780}{[arXiv:2305.13780]} 
\item Emmanouil Theodosis and Demba Ba, \textit{Learning Silhouettes with Group Sparse Autoencoders}, Harvard CRISP Preprint. 
\item Eric J.\  Michaud, Ziming Liu, Max Tegmark, \textit{Precision Machine Learning}, Entropy, 2023, 25(1). \href{https://arxiv.org/abs/2210.13447}{[arXiv:2210.13447]} 
\item Michael Skuhersky, Tailin Wu, Eviatar Yemini, Amin Nejatbakhsh, Edward Boyden & Max Tegmark, \textit{Toward a more accurate 3D atlas of C. elegans neurons}, BMC Bioinformatics, Volume 23, Article 195. 
\item Richard Li, Carlos Esteves, Ameesh Makadia, Pulkit Agrawal, \textit{Stable Object Reorientation using Contact Plane Registration}, International Conference on Robotics and Automation 2022. 
\item Andrew K.\  Tan, Max Tegmark, Isaac L.\  Chuang, \textit{Pareto-optimal clustering with the primal deterministic information bottleneck}, Entropy, 2022, 24(6). \href{https://arxiv.org/abs/2204.02489}{[arXiv:2204.02489]} 
\item Ziming Liu, Varun Madhavan, Max Tegmark, \textit{AI Poincaré 2.0: Machine Learning Conservation Laws from Differential Equations}, Physical Review E, 2022, Volume 106, Article 045307. \href{https://arxiv.org/abs/2203.12610}{[arXiv:2203.12610]} 
\item Artan Sheshmani, Yizhuang You, Wenbo Fu, Ahmadreza Azizi, \textit{Categorical Representation Learning and RG flow operators for algorithmic classifiers}, Machine Learning Science and Technology, Volume 4, Number 1, Article 015012. \href{https://arxiv.org/abs/2203.07975}{[arXiv:2203.07975]} 
\item Andrew Ma, Yang Zhang, Thomas Christensen, Hoi Chun Po, Li Jing, Liang Fu, Marin Soljačić, \textit{Topogivity: A Machine-Learned Chemical Rule for Discovering Topological Materials}, American Chemical Society Publications. \href{https://arxiv.org/abs/https://arxiv.org/abs/2202.05255}{[arXiv:https://arxiv.org/abs/2202.05255]} 
\item Alexander Lin, Andrew H.\  Song, Demba Ba, \textit{Mixture Model Auto-Encoders: Deep Clustering through Dictionary Learning}, ICASSP 2022 - 2022 IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), 2022, pp. 3368-3372. \href{https://arxiv.org/abs/2110.04683}{[arXiv:2110.04683]} 
\item Ge Yang, Anurag Ajay, Pulkit Agrawal, \textit{Overcoming the Spectral Bias of Neural Value Approximation}, ICLR 2022 Conference Proceedings. \href{https://arxiv.org/abs/2206.04672}{[arXiv:2206.04672]} 
\item Samantha D'Alonzo, Max Tegmark, \textit{Machine-Learning media bias}, PLOS ONE, 2022, Volume 17, Issue 8, Article e0271947. \href{https://arxiv.org/abs/2109.00024}{[arXiv:2109.00024]} 
\item Peter Y.\  Lu, Joan Ariño, Marin Soljačić, \textit{Discovering Sparse Interpretable Dynamics from Partial Observations}, Communications Physics, 2022, Vol 5, Article 206. \href{https://arxiv.org/abs/2107.10879}{[arXiv:2107.10879]} 
\item Yuanming Hu, Jiafeng Liu, Xuanda Yang, Mingkuan Xu, Ye Kuang, Weiwei Xu, Qiang Dai, William Freeman, Fredo Durand, \textit{QuanTaichi: A Compiler for Quantized Simulations}, ACM Transactions on Graphics, Volume 4, Article 182. 
\item Daniel A.\  Roberts, Sho Yaida, Boris Hanin, \textit{The Principles of Deep Learning Theory}, Cambridge University Press (Book), 2022. \href{https://arxiv.org/abs/2106.10165}{[arXiv:2106.10165]} 
\item Alexander Lin, Andrew H.\  Song, Berkin Bilgic, Demba Ba, \textit{Covariance-Free Sparse Bayesian Learning}, IEEE Transactions on Signal Processing, volume 70. \href{https://arxiv.org/abs/2105.10439}{[arXiv:2105.10439]} 
\item Samuel Kim, Peter Y.\  Lu, Charlotte Loh, Jamie Smith, Jasper Snoek, Marin Soljačić, \textit{Scalable and Flexible Deep Bayesian Optimization with Auxiliary Information for Scientific Problems}, Transactions on Machine Learning Research, September 2022. \href{https://arxiv.org/abs/2104.11667}{[arXiv:2104.11667]} 
\item Dor Verbin, Todd Zickler, \textit{Field of Junctions: Extracting Boundary Structure at Low SNR}, IEEE/CVF International Conference on Computer Vision, 2021. \href{https://arxiv.org/abs/2011.13866}{[arXiv:2011.13866]} 
\end{itemize}